Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-01-14 paper.tex
Various bug fixes

Using this property we define maps $i^n_{n+1}\from \Sk^1 K_n$ to $\Sk^1K_{n+1}$
as follows.

@@

\begin{theorem}
  If $G$ satisfies $\Sd_M$ for all $M$ then $\boundary G$ is locally simply
  connected.
\end{theorem}

>>>>

Using this property we define maps $i^n_{n+1}\from \Skel_1 K_n$ to
$\Skel_1K_{n+1}$ as follows.

@@

\begin{restatable}{theorem}{ddagimpliesLCd}
  If $G$ satisfies $\Sd_M$ for all $M$ then $\boundary G$ is locally simply
  connected.
\end{restatable}
